---
title: "Keywords from the UniProt database"
author: "Zuguang Gu (z.gu@dkfz.de)"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Keywords from the UniProt database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


UniProt database provides a list of controlled vocabulary represented as keywords
for genes or proteins (https://www.uniprot.org/keywords/). This is useful for summarizing gene functions in a compact way. This package
provides data of keywords hierarchy and gene-keywords relations.


First load the package.

```{r}
library(UniProtKeywords)
```

The package has five datasets. The first contains basic information of every keyword term:

```{r}
data(kw_terms)
length(kw_terms)
kw_terms[["Cell cycle"]]
```


The other four contain hierarchical structures of the keyword terms:

```{r}
data(kw_parents)
kw_parents[1:2]

data(kw_children)
kw_children[1:2]

data(kw_ancestors)
kw_ancestors[1:2]

data(kw_offspring)
kw_offspring[1:2]
```

The **UniProtKeywords** package has also compiled genesets of keywords for some species, which can get by the function `load_keyword_genesets()`.
The argument is the taxon ID of a species:

```{r}
gl = load_keyword_genesets(9606)
gl[1:2]
```

Session info:

```{r}
sessionInfo()
```
